HO unification from object language to meta language

### 2024-04-03 paper/main.tex
update proof cor 8.3

\begin{proof}[Proof sketch]
  By contradiction,\noteE{we assume to have a link} if $m = 0$, then the original \Fo{} term
  has the shape \elpiIn{fapp[fuva M | Ag]} where \elpiIn{Ag} is a list of
  distinct names (i.e. the list \elpiIn{Extra} is empty). This case is however
  captured by rule~\ref{rule:complam} (from \cref{sec:compilation}) and no
  \linkbeta is produced: a contradiction.\noteE{since we started by assuming we had a link}
\end{proof}

>>>>

\begin{proof}[Proof sketch]
  Assume we have a \linkbeta, by contradiction, if $m = 0$, then the original
  \Fo{} term has the shape \elpiIn{fapp[fuva M | Ag]} where \elpiIn{Ag} is a
  list of distinct names (i.e. the list \elpiIn{Extra} is empty). This case is
  however captured by rule~\ref{rule:complam} (from \cref{sec:compilation}) and
  no \linkbeta is produced which contradicts our initial assumption.
\end{proof}
